---
title: "writing_functions"
author: "Lorraine Kwok"
date: "October 24, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

We're going to write some functions. 

z-scores
```{r}
x = rnorm(n = 30, mean = 4, sd = 2.3)
x_again = rnorm(n = 30, mean = 6, sd = .3)

(x - mean(x)) / sd(x)
(x_again - mean(x_again)) / sd(x_again)
```

Now a function. 
```{r}
z_score = function(x_arg) {
  
  if (!is.numeric(x_arg)) {
    stop("x should be numeric")
   } else if (length(x_arg) < 3) {
      stop("x should be longer than 3")
    }

  
 (x_arg - mean(x_arg)) / sd(x_arg)
 
}
```

Try out the function. 

```{r, error = TRUE}
z_score(x_arg = x_again)

z_score(x_arg = 3)
z_score(x_arg = "my name is jeff")
z_score(x_arg = c(TRUE, TRUE, FALSE, TRUE))
z_score(x_arg = iris)
```

## Multiple outputs

```{r}
mean_and_sd = function(input_x) {
  
  if (!is.numeric(input_x)) {
    stop("x should be numeric")
   } else if (length(input_x) < 3) {
      stop("x should be longer than 3")
   }
  
  list(
  mean_input = mean(input_x),
  sd_input = sd(input_x),
  z_score = (input_x - mean(input_x)) / sd(input_x)
  )
  
}
```

test this function

```{r}
mean_and_sd(input_x = x_again)
```

Lists are nice because they allow you to keep track of things that are not just numbers 

## Multiple inputs

```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

sim_data %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```

This is a simulated dataset.

```{r}
sim_regression = function(n, beta0, beta1) {
  
  sim_data = tibble(
  x = rnorm(n, mean = 1, sd = 1),
  y = beta0 + beta1 * x + rnorm(n, 0, 1)
 )


 ls_fit = lm(y ~ x, data = sim_data)
  
 tibble(
   beta0_hat = coef(ls_fit)[1], 
   beta1_hat = coef(ls_fit)[2]
 )
 
}

sim_regression(n = 3000, beta0 = 17, beta1 = -3)

sim_regression(3000, 2, 3)
```

arguments can have default functions too (beta0 and beta1 will change only if user changes it)

```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = tibble(
  x = rnorm(n, mean = 1, sd = 1),
  y = beta0 + beta1 * x + rnorm(n, 0, 1)
 )


 ls_fit = lm(y ~ x, data = sim_data)
  
 tibble(
   beta0_hat = coef(ls_fit)[1], 
   beta1_hat = coef(ls_fit)[2]
 )
 
}

sim_regression(n = 3000, beta0 = 17, beta1 = -3)

sim_regression(3000, 2, 3)
sim_regression(3000)
sim_regression(n = 14, beta0 = 24)
```

## Scrape lots of napoleon

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

Now as a function

```{r}
read_page_reviews = function(page_url) {

  dynamite_html = read_html(page_url)
  
  review_titles = dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  review_stars = dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text()
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  
  reviews
  
}

```

```{r}
read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1")

read_page_reviews("https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2")
```

